Twisted eleven-dimensional supergravity

### 2023-12-15 index 2/intro.tex
agt

We propose similar statements at the level of the minimal twist. 
We fix a complex surface $S$ together with a pair of complex vector bundles $L,W \to S$ of ranks one and two respectively, satisfying the condition that $X = \text{Tot} (L \oplus W)$ is a Calabi--Yau fivefold.
The twisted eleven-dimensional supergravity lives on the eleven-manifold $\R \times X$.

@@

Choosing a fiberwise hermitian metric affords a norm map 
\[
\pi \colon Z \to \R_{+}
\] 
whose fiber away from $0$ is the total space of the unit sphere bundle.
The pushforward factorization algebra $\pi_{*}\Obs_{1}$ is a stratified factorization algebra on the non-negative half-line $\R_+ = \{t \geq 0\}$. 
We can tweak this factorization algebra slightly which gives rise to a constructible factorization algebra on $\R_+$.
In turn, this is equivalent to a pair of an associative algebra (which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold which is the total space of the unit sphere bundle) together with a module for this algebra.

In \cite{SWtensor} it is shown that in the case where $L$ is the trivial bundle, the naive dimensional reduction (where we discard higher Kaluza--Klein modes along the circle fiber) along 
\beqn
S \times \C \to S \times \R_+
\eeqn
agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ supersymmetric Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector.

If we keep track of Kaluza--Klein modes, our expectation is that the full dimensional reduction $\pi_{*}\Obs_{1}|_{\R_{>0}}$ includes contributions from instanton operators.\footnote{The instanton charge turns out to be identical to the winding number around $S^1$.} Moreover, the module at zero $\pi_{*}\Obs_{1}|_{0}$ ought to be identified with the Hilbert space of the minimal twist of five-dimensional $\cN = 2$ gauge theory. We are left with the following conjecture.

\begin{conj}
\label{conj:AGT1}
Let $\operatorname{Higgs}_{GL(1)} (S,W)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields has coefficients in the rank two bundle $W$.
The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ that we have just discussed acts on the space of functions on this moduli space
\beqn
\cO \left(\operatorname{Higgs}_{GL(1)} (S,W)\right) .
\eeqn
\end{conj}

We emphasize that the moduli space in question is really sensitive to the complex geometry of the entire fivefold $X$, at least in the neighborhood of the total space of~$L$.

While we leave the precise relationship of this conjectural action with the usual abelian AGT correspondence to future work, we can highlight some compatibilities. Above, we have mentioned a particular deformation of the observables of the six-dimensional $\cN = (2,0)$ theory by an explicit Maurer--Cartan element in the residual superconformal algebra $\lie{osp}(6|2)$. We point out that this deformation is of the same spirit considered in \cite{BeemEtAl}. For a particular choice of the fivefold $X$, one can identify (though we do not do that in this paper) this deformation of $\pi_{*} \Obs_1|_{\R_{>0}}$ with the Heisenberg algebra.

>>>>

We propose similar statements at the level of the minimal twist. 
We fix a complex surface $S$ together with a triple of complex line bundles $L, L_1, L_2\to S$ satisfying the condition that $X = \text{Tot} (L \oplus L_1 \oplus L_2)$ is a Calabi--Yau fivefold. 
The twisted eleven-dimensional supergravity lives on the eleven-manifold $\R \times X$.

@@

Choosing a fiberwise hermitian metric affords a norm map 
\[
\pi \colon Z \to \R_{+}
\] 
whose fiber away from $0$ is the total space of the unit sphere bundle.
The pushforward factorization algebra $\pi_{*}\Obs_{1}$ is a stratified factorization algebra on the non-negative half-line $\R_+ = \{t \geq 0\}$.

In turn, this is equivalent to a pair of an associative algebra (which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold which is the total space of the unit sphere bundle in $L$) together with a module for this algebra.

In \cite{SWtensor} it is shown that in the case where $L$ is the trivial bundle, the naive dimensional reduction (where we discard higher Kaluza--Klein modes along the circle fiber) along 
\beqn
S \times \C \to S \times \R_+
\eeqn
agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ supersymmetric Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector. Keeping track of Kaluza-Klein modes, one expects that the dimensional reduction $\pi_{*}\Obs_{1}|_{\R_{>0}}$ receives contributions from instanton operators codified by way of a certain Chern-Simons term. Let us explicate how these contributions manifest in the dimensionally reduced factorization algebra.

Nonperturbatively, five-dimensional $\cN=2$ super Yang-Mills has a topological $U(1)$ symmetry, charges under which are instanton number. This charge can be measured by introducing a background gauge field $\theta$ for this symmetry and adding a Chern-Simons term of the form 
\[
\int Tr (\theta\wedge F\wedge F) = \int c_1 (L) \wedge CS (A)
\]
 to the action, where $F$ is the curvature of the five dimensional gauge field $A$ and $CS(A)$ denotes the corresponding Chern-Simons three-form. An ingredient in identifying the dimensional reduction of the six-dimensional $\cN=(2,0)$ theory on a circle with five-dimensional $\cN= (2,0)$ is an identification of the above $U(1)$-charge with one keeping track of Kaluza-Klein modes along the circle fiber of $Z \to S\times \R_{>0}$. Accordingly, the dimensional reduction along the circle fiber of a nontrivial line bundle will include the above term in the action.

We claim that this term crucially enters into the description of the module at zero $\pi_{*}\Obs_{1}|_{0}$. This module ought to be identified with the Hilbert space of the minimal twist of five-dimensional $\cN = 2$ gauge theory, which can be calculated by geometrically quantizing the phase space. We will see that the phase space can naturally be written as a twisted cotangent bundle, where the twist depends on the above Chern-Simons term.

Perturbatively, the phase space is described by the following local Lie algebra. 
\beqn
\begin{tikzcd}
\underline{-2} & \underline{-1} & \underline{0} \\
& \Omega_S^{0,\bullet}\arrow[dd, "c_1(L)\wedge\partial"] & \\
\Omega_S^{0,\bullet}(L_2)& & \Omega^{0,\bullet}_S(L_1\otimes L_2) \\
& \Omega_S^{0,\bullet}(K_S)  &
\end{tikzcd}
\eeqn

We thus see that the phase space has a natural polarization whose base is given by $\Omega^{0,\bullet}_S(L_2)[2] \oplus \Omega^{0,\bullet}[1]$. The differential made explicit deforms the symplectic structure to that of a twisted cotangent bundle.

Globally, we can describe an algebro-geometric model for the polarized phase space as 
\[
T^*_\Pi \operatorname{Higgs} _{GL(1)} (S, L_2)
\]
where $\operatorname{Higgs}_{GL(1)} (S, L_2)$ is the moduli of pairs of a rank 1 torsion free sheaf $Z$ on $S$ and a section $\phi \in \Gamma (Z\otimes L_2)$. We will call these \textit{rank 1 $L_2$ twisted Higgs sheaves}. Letting $TFS_1(S)$ denote the moduli of rank 1 torsion free sheaves on $S$, there is a natural projection 
\[\operatorname{Higgs}_{GL(1)} (S, L_2)\] and a diagram
\beqn
\begin{tikzcd}
S\times TFS_1 (S)\ar[r, "\pi_2"]\ar[d, "\pi_1"] & TFS_1 (S) \\
S
\end{tikzcd}
\eeqn
The global symplectic form on the phase space is given by 
\[
p^*{\pi_2}_*\left (\pi_1^* c_1 (L) \wedge ch_2 (Z_{univ})\right )
\]
where $Z_{univ}$ denotes the universal rank 1 torsion free sheaf.

We are thus left with the following conjecture.

\begin{conj}
\label{conj:AGT1}
Let $\operatorname{Higgs}_{GL(1)} (S,L_2)$ denote the moduli space of rank 1 $L_2$-twisted Higgs sheaves on $S$. The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ acts on the coherent cohomology 
\beqn
H^\bullet \left(\operatorname{Higgs}_{GL(1)} (S,L_2), \Theta \right) .
\eeqn
of a certain line bundle $\Theta$ whose first chern class is the above symplectic form.
\end{conj}

While we leave the precise relationship of this conjectural action with the usual abelian AGT correspondence to future work, we can highlight some compatibilities \surya{FINISH}. Above, we have mentioned a particular deformation of the observables of the six-dimensional $\cN = (2,0)$ theory by an explicit Maurer--Cartan element in the residual superconformal algebra $\lie{osp}(6|2)$. We point out that this deformation is of the same spirit considered in \cite{BeemEtAl}. For a particular choice of the fivefold $X$, one can identify (though we do not do that in this paper) this deformation of $\pi_{*} \Obs_1|_{\R_{>0}}$ with the Heisenberg algebra.
